Comments on Latent Ranking

### 2021-04-21 output_scripts/aug_updates.Rmd
add updates from aug to push to main

for(current_cohort in 1:10){
  ## load true model fit
  load(paste(data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))

@@

  ## load permuted model fit
  load(paste(data_path,cohort_names[current_cohort],
             "/permute_cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))

@@

```
There does appear to be little to no structure in the estimated parameters 
after this permutation. For example, all `gamma` and `zeta` parameters display 
similar values, compared to the range seen in the original data. Similarly,
there is little to no correlation in the rankings 
obtained from the true events and the permuted events.

>>>>

for(current_cohort in 1:10){
  ## load true model fit
  load(paste(data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",sep=''))

@@

  ## load permuted model fit
  load(paste(data_path,cohort_names[current_cohort],
             "/permute_cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",sep=''))

@@

There does appear to be little to no structure in the estimated parameters 
after this permutation. For example, all `gamma` and `zeta` parameters display 
similar values, compared to the range seen in the original data. Similarly,
there is little to no correlation in the rankings 
obtained from the true events and the permuted events.
